Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-03 src/article.tex
Rename section [Evaluation -> Models comparison]
Add bibliography about invertedIndexTechnique

    For a long time, term-based models were used for the first stage of search, which showed high
    efficiency due to simple logic and the use of an inverse index
    \cite{termBasedModelEfficiency1, termBasedModelEfficiency2}.
    However, this approach has drawbacks in the form of vocabulary mismatch
    \cite{vocabularyMismatch1, vocabularyMismatch2} and lack of consideration of the order of
    terms in documents \cite{ignoringTermOrdering}.
    Thus, term-based models can lose some of the relevant documents at the very beginning.
    To get rid of these limitations, various solutions have been proposed, such as vocabularies
    of synonyms or query \cite{queryExp1,queryExp2,queryExp3,queryExp4} and document
    \cite{docExp1, docExp2, docExp3} expansion.
    However, progress has been limited due to the fact that these approaches still remain in
    the term-based paradigm and inherit its limitations.

@@

    During the search, the query is broken down into terms in the same way as documents, then
    they are used as keys in the inverted index to find the corresponding documents.
    The more query terms are found in a document, the more suitable it is for re-ranking.

@@

    \section{Evaluation}

@@

    The comparison results are shown in the Table \ref{tab:evaluation}.
    Mean Reciprocal Rank (MMR@10) is used as a metric for assessing accuracy.

>>>>

    For a long time, term-based models were used for the first stage of search, which showed high
    efficiency \cite{termBasedModelEfficiency1, termBasedModelEfficiency2} due to simple logic
    and the use of an inverse index.
    However, this approach has drawbacks in the form of vocabulary mismatch
    \cite{vocabularyMismatch1, vocabularyMismatch2} and lack of consideration of the order of
    terms in documents \cite{ignoringTermOrdering}.
    Thus, term-based models can lose some of the relevant documents at the very beginning.
    To get rid of these limitations, various solutions have been proposed, such as vocabularies
    of synonyms or query \cite{queryExp1,queryExp2,queryExp3,queryExp4} and document
    \cite{docExp1, docExp2, docExp3} expansion.
    However, progress has been limited due to the fact that these approaches still remain in
    the term-based paradigm and inherit its limitations.

@@

    During the search, the query is broken down into terms in the same way as documents, then
    they are used as keys in the inverted index to find the corresponding documents.
    The more query terms are found in a document, the more suitable it is for re-ranking.
    For details on the inverted index technique, see
    \cite{invertedIndexTechnique1, invertedIndexTechnique2}

@@

    \section{Models comparison}

@@

    The comparison results are shown in the Table \ref{tab:evaluation}.
    Mean Reciprocal Rank (MRR@10) is used as a metric for assessing accuracy.
